Reviewer comments from PeerJ

### 2015-03-23 PeerJResponse.tex
Edits
LV edits to response and text

\res{We have addressed comments from Reviewer 2 regarding the validity of the PCR assays. Sequencing of PCR products were not sequenced, but primer combinations for each of the 2 PCRs produced the expected sized bands. Primers were designed using previously sequenced teosinte and maize sequences provided by John Doebley, and were initially tested in both maize and teosinte for validity.  We have clarified this point in the text \lev{text, line numbers here} and have added additional labeling to the gel image (Figure 2).}

@@

\res{We feel that the addition of state lines makes the figure too busy and difficult to read. However, we have added labels to the 4 focal Jalisco populations (La Mesa (MSA), San Lorenzo (SLO), Ejutla A (EjuA), and Ejutla B (EjuB)).}

\mbh{I don't think state lines would make the figure too busy.  Is the issue that you no longer have access to ArcGIS, LV?  Jeff, do you think it's worth trying to redo this in R or do you think Todd will be fine with this response?}

>>>>

\res{We have addressed comments from Reviewer 2 regarding the validity of the PCR assays. Sequencing of PCR products were not sequenced, but primer combinations for each of the 2 PCRs produced the expected sized bands. Primers were designed using previously sequenced teosinte and maize sequences provided by John Doebley, and were initially tested in both maize and teosinte for validity.  We have clarified this point in the text page 4, lines 75-87 and have added additional labeling to the gel image (Figure 2).}

@@

\res{We have edited this figure (now Figure 2) to include state lines and have added labels to the 4 focal Jalisco populations (La Mesa (MSA), San Lorenzo (SLO), Ejutla A (EjuA), and Ejutla B (EjuB)).}
